Hydras \& Co.

### 2022-04-06 doc/gaia-chapter.tex
simplification of notations in theories/gaia

\section{Already ported definitions and lemmas}

\textbf{These tables are still in construction.}

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Types for ordinals less than $\epsilon_0$}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Hydras & page & Gaia-Hydras& page& Description \\\hline
  \texttt{T1.T1} 
       &  \pageref{types:T1}
              & \texttt{CantorOrdinal.T1}
                           &  & ordinal terms \tnote{1} \\

  \texttt{E0.E0}
       & \pageref{types:E0}
              & \texttt{T1Bridge.E0}
                           & \pageref{sect:E0-gaia-hydras}
                                 & ordinal terms in Cantor normal form \\

  \texttt{ON\_Finite.t}
       & \pageref{def:Finite-ord-type}
              & \ssreflect's finite ordinals \tnote{2}&  & ordinals below $\omega$ \\
\hline
\end{tabular}
\begin{tablenotes}
  \item[1] From \gaia library.
   \item[2] From \ssreflect/\mathcomp libraries.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Hydras & page & Gaia-Hydras& page& Description \\\hline
  \texttt{T1.zero}
       &  \pageref{types:T1}
              & \texttt{CantorOrdinal.zero \tnote{1}}
                           &  & The ordinal $0$  \\

\hline
\end{tabular}
\begin{tablenotes}
  \item[1] From \gaia library.
   \item[2] From \ssreflect/\mathcomp libraries.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

% \section{Already ported definitions and lemmas}

% \textbf{These tables are still in construction.}

% \begin{table}[H]
%   \centering
%   \begin{threeparttable}
%     \caption{Types for ordinals less than $\epsilon_0$}
% \begin{tabular}{|r | c|c|c|c|l|}
% \hline
% Hydras & page & Gaia-Hydras& page& Description \\\hline
%   \texttt{T1.T1} 
%        &  \pageref{types:T1}
%               & \texttt{CantorOrdinal.T1}
%                            &  & ordinal terms \tnote{1} \\

%   \texttt{E0.E0}
%        & \pageref{types:E0}
%               & \texttt{T1Bridge.E0}
%                            & \pageref{sect:E0-gaia-hydras}
%                                  & ordinal terms in Cantor normal form \\

%   \texttt{ON\_Finite.t}
%        & \pageref{def:Finite-ord-type}
%               & \ssreflect's finite ordinals \tnote{2}&  & ordinals below $\omega$ \\
% \hline
% \end{tabular}
% \begin{tablenotes}
%   \item[1] From \gaia library.
%    \item[2] From \ssreflect/\mathcomp libraries.
% \end{tablenotes}
% \end{threeparttable}
% \end{table}

% \begin{table}[H]
%   \centering
%   \begin{threeparttable}
%     \caption{Main constants}
% \begin{tabular}{|r | c|c|c|c|l|}
% \hline
% Hydras & page & Gaia-Hydras& page& Description \\\hline
%   \texttt{T1.zero}
%        &  \pageref{types:T1}
%               & \texttt{CantorOrdinal.zero \tnote{1}}
%                            &  & The ordinal $0$  \\

% \hline
% \end{tabular}
% \begin{tablenotes}
%   \item[1] From \gaia library.
%    \item[2] From \ssreflect/\mathcomp libraries.
% \end{tablenotes}
% \end{threeparttable}
% \end{table}
